Bayesian Inference Using Sequential Monte-Carlo Algorithm for Dynamic System Models

### 2020-08-01 MSc-dissertation.tex
New fig

    \caption{Simulated trajectory from the last population of model 1, 2 and 3}
    \label{fig:result123}

>>>>

    \caption[Simulated trajectory from the 20th population of model 1, 2 and 3]%
    {Simulated trajectory from the last population of model 1, 2 and 3. Error bar indicates SEM. 500 randomly chosen particles from last population are used to generate a sequence of trajectories where mean and inter-quartile range are calculated from}
    \label{fig:result123}
